Nail: A practical interface generator for data formats

### 2014-09-10 paper/osdi14/design.tex
4.3 nits

Nail provides only one built-in combinator that uses dependent fields, \cc{n_of}, which acts like
the \cc{many} combinator, except it represents an exact number, specified in the dependent field, of
repetitions, as opposed as many repetitions as possible. For example, DNS labels, which
are encoded as a length followed by
a value are described in line 38 of the DNS grammar.
Other dependencies, such as offset fields or checksums, are not handled directly by combinators, but
through  transformations, as we describe next.

>>>>

Nail provides only one built-in combinator that uses dependent fields, \cc{n_of}, which acts like
the \cc{many} combinator, except it represents an exact number, specified in the dependent field, of
repetitions, as opposed to as many repetitions as possible. For example, DNS labels, which
are encoded as a length followed by
a value, are described in line 38 of the DNS grammar.
Other dependencies, such as offset fields or checksums, are not handled directly by combinators, but
through  transformations, as we describe next.
